Automatic Matching of Bullet Lands

### 2016-01-01 imaging-paper.Rnw
speed consideration

\item add: should we add a paragraph on the speed of the evaluation? - separate out into pre-processing (needs to be done once) and matching (pairwise comparison of lands). If we only do bullet matching, we could speed this process up by eliminating some land comparisons.

>>>>

\item add: should we add a paragraph on the speed of the evaluation? - separate out into pre-processing (needs to be done once) and matching (pairwise comparison of lands). If we only do bullet matching, we could speed this process up by eliminating some land comparisons. - Thinking about this more, I'm against it. The speed massively depends on the kind of computer used - the important thing is, that on a server all of these calculations are very fast -- even my machine can do 11 comparisons per second, if the files are pre-processed. Pre-processing might take a couple of seconds - at most 20-30 seconds for each bullet land. That is an initial cost one has to pay.
